---
title: "One-way Analysis of Variance"
author: "Data Analysis in Sociology"
date: "3/24-25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Problem 1

Is the level of alcohol sales the same across the Federal Districts of Russia? 

The data come from <https://rosstat.gov.ru/> and <https://www.kaggle.com/dwdkills/alcohol-consumption-in-russia>

Data file: `alcohol_districts.csv`

```{r}
library(readr)
alcohol_districts <- read_csv("~/0_teaching/DAS 2023/DAS 2023/data/alcohol_districts.csv")
alcohol_districts
```


Create an index showing the average sales of all the types of alcohol per region. Use `rowMeans()` to calculate the mean across several columns.

```{r}
# Calculate the average sales across all alcohol types
avg_sales <- rowMeans(alcohol_districts[, c("wine", "beer", "vodka", "champagne", "brandy")])

# Add the average sales as a new column to the data frame
alcohol_districts$avg_sales <- avg_sales

# Use aggregate() to calculate the average sales by region
region_avg_sales <- aggregate(avg_sales ~ region, data = alcohol_districts, mean)

# Print the results
print(region_avg_sales)
```

Compare the average value of the index across the Federal Districts **in 2016**. 

```{r}
alcohol_2016 <- alcohol_districts[alcohol_districts$year == 2016,]

# Calculate the mean of the average sales for each Federal District
district_avg_sales <- aggregate(avg_sales ~ district, data = alcohol_2016, mean)

# Print the results
print(district_avg_sales)
```

Now try a new way of visualising pairwise comparisons. Read the example for the `ggbetweenstats()` function here and adapt the non-parametric test used in this example: <https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggbetweenstats.html>.

```{r}
#install.packages("ggstatsplot")
library(ggstatsplot)
alcohol_2016
```
```{r}
ggbetweenstats(
  data = alcohol_2016,
  x = district, ## grouping/independent variable
  y = avg_sales, ## dependent variables
  type = "np", ## type of statistics
  xlab = "District", ## label for the x-axis
  ylab = "Avarage Alcohol Sales", ## label for the y-axis
  plot.type = "violin", ## type of plot
  outlier.tagging = TRUE, ## whether outliers should be flagged
  outlier.coef = 1.5, ## coefficient for Tukey's rule
  outlier.label = region, ## label to attach to outlier values
  outlier.label.args = list(color = "red"), ## outlier point label color
  ## turn off messages
  title = "Comparison of alcohol sales across districts (Year: 2016)",
)
```




## Problem 2

For tasks 2-3, use the file `so2.csv` from the data folder. The data set contains the result of a survey of software developers using the StackOverflow website.

How is the subjective level of competence in programming related to coding experience?

Do the most experienced developers feel they are the most proficient?

Examine this relationship visually, then run a suitable statistical test, and show the effect size. 

Variables: `ImpSyn`, `YearsCodePro`.


```{r}
library(readr)
so <- read_csv("~/0_teaching/DAS 2023/DAS 2023/data/so.csv")
so
```


Now try a new way of visualising distribution of numeric variable across groups-- a ridgeplot. 

Read the example for the `geom_ridgeline` function here and adapt the code to our data: <https://cran.r-project.org/web/packages/ggridges/vignettes/introduction.html> (go to the "Density ridgeline plots" section)

```{r}
# install.packages("ggridges")
library(ggridges)
# put your code here
```



## Problem 3

Are the more experienced programmers seriously older?

Compare the age of respondents by their coding experience.

First, visualise the relationship, then run a suitable statistical test, and show the effect size. 

```{r}
# put your code here
```


Finally, create a visualization with all the effects shown in the picture. Use `ggbetweenstats()`.

Variables: `ImpSyn`, `Age`.

```{r}
library(ggstatsplot)
# put your code here
```












