---
title: "Seminar 3"
author: "Aleksei Sorbale"
date: "2023-02-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Base R visualization of descriptive statistics**

#### Task 1. Histogram

```{r}
##Random normal distribution

seminar_3_norm<-rnorm(10000)
summary(seminar_3_norm)

hist(seminar_3_norm, breaks=100, main="Histogram for Seminar 3",
     xlab="Seminar 3 normal distribution")# breaks = the intervals between the columns
abline(v = 0.008839, col="red", lwd=2, lty=2)# v=value, col=color, lwd=line width, lty=type of the line 


#dev.off()#remove all visualization
```

#### Task 2. Boxplots

```{r}
Karelia <- read.csv("Data/Karelia2016.csv", sep=';')

attach(Karelia)

boxplot(United_Russia, main = "Votes for United Russia in Karelia on the 2016 Duma elections",
xlab = "", ylab ="Number of votes", col = "blue", border = "black")

boxplot(United_Russia, KPRF, LDPR, A_Just_Russia, 
         main = "Votes for major parliamentary parties on the 2016 Duma elections in Karelia", 
         names = c("United Russia", "CPRF", "LDPR", "A Just Russia"),
         col = c("lightblue", "red", "gold1", "darkolivegreen1"), border = "brown")

```

#### Task 3. Scatterplot

```{r}

plot(KPRF, main = "Votes for CPRF in Karelia on the 2016 Duma elections",
xlab = "№ of PEC", ylab ="Percentage of votes", col = "red")

detach(Karelia)
```

## Visualization with ggplot2

```{r}
library(ggplot2)
library(ggthemes)

elections <- read.csv("Data/French_Presidential_Election_2017.csv", sep = ";")
```

### Task 1. Histogram

The 'fill' argument allows to fill the entire histogram with color. To change the color of the histogram borders, you must also specify the \`col' argument. To change the transparency level of the color used for the fill, use the 'alpha' argument.

Here are ggplot2 customizing materials: <https://ggplot2.tidyverse.org/index.html>

```{r}
p<-ggplot() +
  geom_histogram(data = elections, aes(x = Voters), binwidth = 5)#binwidth = change the width of bars
p

#### Add captions on the axes and the title of the graph

p + ggtitle("Distribution of voters") + 
  xlab("Number of voters") + 
  ylab("Quantity")


#### Change the appearance of the chart: fill, border colors, transparency

a<-ggplot() +
  geom_histogram(data = elections, aes(x = Voters), binwidth = 5, fill="#008080", col="#483D8B", alpha = 0.5)  + 
  ggtitle("Distribution of voters") + 
  xlab("Number of voters") + 
  ylab("Quantity")
a

#### Change the plot's theme.

a + theme_bw()
a + theme_tufte()
```

### Task 2. Boxplot

```{r}
c<-ggplot() +
  geom_boxplot(data = elections, aes(y = Voters), col = "#E52B50", fill = "#F0F8FF") + 
  xlab(" ") + 
  ylab("Number of voters") + 
  ggtitle("Distribution of voters") + 
  theme_bw()  
c

##Comparison of distributions of different constituencies.

d<-ggplot() +
  geom_boxplot(data = elections, aes(x = Constituency, y = Voters)) + 
  xlab(" ") + 
  ylab("Numer of voters") + 
  ggtitle("Distribution of voters for different constituencies") + 
  theme(axis.text.x=element_text(angle=90,size=8))
d

## We can add an additional 'fill' argument to put multiple categorical variables in a single boxplot.

r<-ggplot() +
  geom_boxplot(data = elections, aes(x = Constituency, y = Voters, fill=Sex)) + 
  xlab(" ") + 
  ylab("Numer of voters") + 
  ggtitle("Distribution of voters for different constituencies by gender") + 
  theme(axis.text.x=element_text(angle=90,size=8))
r
```

### Task 3. Scatterplot

```{r}
o<-ggplot() +
  geom_point(data = elections, aes(x = Abstentions, y = Voters)) +
  xlab("Abstentions") +
  ylab("Number of voters") +
  ggtitle("Distribution of voters in different departments")
o

### Change the shape depending on the group (same with color)

o<-ggplot() +
  geom_point(data = elections, aes(x = Abstentions, y = Voters, shape = Sex)) +
  xlab("Abstentions") +
  ylab("Number of voters") +
  ggtitle("Distribution of voters in different departments") +
  theme_bw()
o
```

### Task 4 Combine all the plots on one graph

```{r}
library(cowplot)
Frenchplots <- plot_grid(a, r, o)
Frenchplots
```

### Practice. 2016 parliamentary elections: UR (ggplot2)

1.  Import the dataset "ENPG2016.csv
2.  Build a histogram for the variable 'Turnout'
3.  Customize the histogram: give it a title (any relevant) and y caption (any relevant), change its basic ('fill') and bars' borders ('col') colors, change the width of bars (any value relevant)
4.  Change the histogram's theme
5.  Build a scatterplot for the variables 'Turnout'(x-axis) and 'ER' (y-axis)
6.  Customize the scatterplot: give it a title (any relevant) and x-y captions (any relevant), change its basic color
7.  Combine a histogram and a scatterplot on one graph with cowplot package
```{r}
install.packages("tidyverse")
library("tidyverse")
```

```{r}
ENPG2016 <- read_delim("C:/Users/Alex/OneDrive/Документы/0_HSE_study/колы/3/Data/ENPG2016.csv", 
    delim = ";", escape_double = FALSE, col_types = cols(Turnout = col_number(), 
        ER = col_number(), KPRF = col_number(), 
        LDPR = col_number(), SR = col_number(), 
        KR = col_number(), Yabloko = col_number(), 
        RPPS = col_number(), Rodina = col_number(), 
        PR...11 = col_number(), Zelenye = col_number(), 
        PNS = col_number(), PR...14 = col_number(), 
        GP = col_number(), GS = col_number()), 
    trim_ws = TRUE)
ENPG2016
```

```{r}
t<-ggplot() +
  geom_histogram(data = ENPG2016, aes(x = Turnout), binwidth = 5, fill="#008080", col="#483D8B", alpha = 0.5)  + 
  ggtitle("Turnout") + 
  xlab("Turnout") + 
  ylab("Frequency")
t + theme_bw()
t
```
```{r}
e<-ggplot() +
  geom_point(data = ENPG2016, aes(x = Turnout, y = ER), col="#008080") + 
  xlab("Turnout") +
  ylab("Votes for ER") +
  ggtitle("Turnout-ER") +
  theme_bw()
e
c<-ggplot() +
  geom_point(data = ENPG2016, aes(x = Turnout, y = ER), col="#008080") +
  geom_point(data = ENPG2016, aes(x = Turnout, y = KPRF), col="#E52B50") +
  geom_point(data = ENPG2016, aes(x = Turnout, y = LDPR), col="#ABC322") +
  geom_point(data = ENPG2016, aes(x = Turnout, y = SR), col="#D9A802") +
  xlab("Turnout") +
  ylab("Votes for Party") +
  ggtitle("Turnout-Party") +
  theme_bw()
c
```
```{r}
library(cowplot)
Russianplot <- plot_grid(t, e)
Russianplot
```

```

