---
title: "Untitled"
output: html_document
date: "2023-05-16"
---

1. Import the dataset Karelia2016.csv.

```{r}
library(readr)
Karelia2016 <- read_delim("~/0_programming/0_prog/0_HSE_study/колы/12/Data/Karelia2016.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
Karelia2016
```
2. Calculate the Turnout variable. 
Tip 1: Turnout variable formula: (Com_Ballots + Home_Ballots)/Voters. 

```{r}
Karelia2016$Turnout <- (Karelia2016$Com_Ballots + Karelia2016$Home_Ballots)/Karelia2016$Voters
Karelia2016
```
3. Calculate the percent of invalid ballots and percent of people, who voted at home (Invalid and Home_Ballots variables are needed here). 

```{r}
Karelia2016$Invalid_p <- Karelia2016$Invalid/Karelia2016$Voters
Karelia2016$Home_Ballots_p <- Karelia2016$Home_Ballots/(Karelia2016$Com_Ballots + Karelia2016$Home_Ballots)
Karelia2016
```
5. Filter the dataset so that only the following variables remain:

• United_Russia: percent of votes for United Russia

• Home_Ballots (or your name): percent of people, who voted at home

• Invalid (or your name): percent of invalid ballots

• Turnout: turnout on the elections in Karelia

```{r}
library(dplyr)

Karelia <- dplyr::select(Karelia2016,United_Russia,Home_Ballots_p, Invalid_p, Turnout)
Karelia
```

6. Round the values in all four variables to 2 decimal places (hundredth).

```{r}
Karelia <- round(Karelia, digits = 2)
Karelia
```

7. Build the following OLS model: DV = United_Russia, IVs = Home_Ballots (or your name), Invalid (or your name), Turnout.
```{r}
model <- lm(United_Russia ~ Home_Ballots_p + Invalid_p + Turnout, data = Karelia)
summary(model)
```

8. Check the model for multicollinearity.

a. Run the test;

```{r}
library(car)
vif(model)
```


b. Indicate whether the problem is present in the model. Explain, what values and/or sections of the test output drove you to the respective conclusion.

```{r}
#The **VIF value** is smaller than 10, therefore there is no multicollinearity in the model
```


c. If multicollineraity is found for the respective IVs, remove one of them (any) from the model

NB: If you identified the problem and fixed it, use the fixed model for further operations!

9. Check the model for the normality of regression residuals’ distribution.

a. Build a Q-Q plot;

Interpret the plot's outlook: which element(s) and their positioning can be used in order to make an assumption about the presence/absence of the problem?

```{r}
qqPlot(model, main="Q-Q Plot for non-corrected model")
```
```{r}
# Most of the observations are out of the range of the blue accaptable range thefore it indicates that the problem exists
```


b. Run the test;

```{r}
summary(powerTransform(Karelia$United_Russia)) ## DV, not model
```


c. Indicate whether the problem is present in the model. Explain, which values and/or sections of the test output drove you to the respective conclusion;

```{r}
#Test for lambda(1) indicates that the p-value is < 0.05 therefore we can reject the H0 (that residuals are normally distributed) so they are not normal and the problem exists
``` 


d. If the problem does exist, fix it with the respective tool.

```{r}
model1<-lm(bcPower(United_Russia, -0.4493)~ Home_Ballots_p + Invalid_p + Turnout, data = Karelia)
summary(model1)
```


NB: If you identified the problem and fixed it, use the fixed model for further operations!

```{r}
qqPlot(model1, main="Q-Q Plot for corrected model")
```


10. Check the model for nonlinearity of relationship between the DV and any of the IVs (one).

a. Build crPlots;

```{r}
crPlots(model1)
```


Interpret the plot's outlook: which element(s) and their positioning can be used in order to make an assumption about the presence/absence of the problem?

```{r}
# The pink should correspond to the blue one. However in our case in Home_Ballots_p we see certain problems with it while in other two variables the pink almost perfectly corresponds with blue line. So probably we have problems but not in all variables. 
```


b. Run the test;

### We need positive values so we need to get rid of minus values

```{r}
Karelia_positive <- Karelia**2+1
Karelia_positive
```


```{r}
boxTidwell(United_Russia ~ Home_Ballots_p, data = Karelia_positive)
```


c. Indicate whether the problem is present in the model. Explain, which values and/or sections of the test output drove you to the respective conclusion;

```{r}
# Problem is present for `Home_Ballots_p` variable as p-value is smaller than 0.05 which indicates the problem of non-linearity statistically does exist
```


d. If the problem does exist, fix it with the respective tool.

```{r}
Karelia_positive$Home_Ballots_p <- (Karelia_positive$Home_Ballots_p)^-279.36
Karelia_positive
```

```{r}
model2<-lm(bcPower(United_Russia, -0.4493)~ Home_Ballots_p + Invalid_p + Turnout, data = Karelia_positive) 
summary(model2)

### I am transforming United_Russia variable due to normality of residuals fixing problem. We have fixed the variable and now using the fixed version of it
```
```{r}
crPlots(model2)
```

11. Use the stargazer package to draw the table with regression output. Do not include R-squared and F- statistic in the table. (for this task use the final version of the corrected model)


```{r}
library(stargazer)

stargazer(model2, 
          type="html",
          model.numbers = FALSE,
          title="Table 1. Regression Results",
          dep.var.labels=c("United Russia"), 
          covariate.labels=c("Home voting","Invalid ballots","Turnout"),
          omit.stat = c("f","rsq"),
          out="Elections_Karelia.html") 
```

