---
title: "Seminar 9"
author: "Aleksei Sorbale"
date: "2023-04-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1. Regression output with `stargazer` package

Calculate the percentage of invalid ballots (`Invalid`), the percentage of voters who voted outside the polling stations (`Home_voting`) and the percentage of absentees (`Absentee_voting`)

```{r}

library(readr)

President2018<-read_delim ("Data/Presidential_elections_2018.csv", 
    delim = ";", escape_double = FALSE, col_types = cols(Number_of_voters = col_number(), 
        Absentee_Ballots = col_number(), 
        Station_Ballots = col_number(), Home_Ballots = col_number(), 
        Home_Box_Ballots = col_number(), 
        Station_Box_Ballots = col_number(), 
        Invalid_votes = col_number(), Valid_votes = col_number(), 
        Baburin_votes = col_number(), Baburin_percent = col_number(), 
        Grudinin_votes = col_number(), Grudinin_percent = col_number(), 
        Zhirinovskii_votes = col_number(), 
        Zhirinovskii_percent = col_number(), 
        Putin_votes = col_number(), Putin_percent = col_number(), 
        Sobchak_votes = col_number(), Sobchak_percent = col_number(), 
        Suraikin_votes = col_number(), Suraikin_percent = col_number(), 
        Titov_votes = col_number(), Titov_percent = col_number(), 
        Yavlinskii_votes = col_number(), 
        Yavlinskii_percent = col_number()), 
    trim_ws = TRUE)

attach(President2018)

```

```{r}

Invalid<-Invalid_votes/(Invalid_votes+Valid_votes)
Home_voting<-Home_Ballots/(Absentee_Ballots + Home_Ballots + Station_Ballots)
Absentee_voting<-Absentee_Ballots/(Absentee_Ballots + Home_Ballots + Station_Ballots)

President2018_new<-cbind(President2018, Invalid, Home_voting, Absentee_voting)
attach(President2018_new)
```

Run four multiple linear regressions

```{r}

regr_Putin<-lm(Putin_percent~Invalid+Home_voting+Absentee_voting)
summary(regr_Putin)

regr_Grudinin<-lm(Grudinin_percent~Invalid+Home_voting+Absentee_voting)
summary(regr_Grudinin)

regr_Zhirinovskii<-lm(Zhirinovskii_percent~Invalid+Home_voting+Absentee_voting)
summary(regr_Zhirinovskii)

regr_Sobchak<-lm(Sobchak_percent~Invalid+Home_voting+Absentee_voting)
summary(regr_Sobchak)
```

Use `stargazer` \-- a package to create smart and informative tables with regression outputs

```{r}

library(stargazer)

stargazer(regr_Putin, regr_Grudinin, regr_Zhirinovskii, regr_Sobchak, 
          type="html",
          model.numbers = FALSE,
          title="Table 1. Regression Results",
          dep.var.labels=c("Putin","Grudinin", "Zhirinovskii", "Sobchak"), 
          covariate.labels=c("Invalid ballots","Home voting","Absentee voting"),
          omit.stat = c("ser", "f"),
          out="Elections-2018.html") # ser = std.error, f= F-statistic

```

```{r}

?stargazer # More information about the function

getwd() # Look where the file with the table was saved
```

## Task 2. Use `stargazer` for descriptive statistics

```{r}

descriptive_statistics<-data.frame(Invalid, Home_voting, Absentee_voting, Putin_percent)

stargazer(descriptive_statistics, type="html",
          title="Descriptive statistics", 
          digits=2, 
          summary.stat=c("n", "mean", "sd", "min", "max","median"),
          out="table_descriptive_statistics.html",
          covariate.labels=c("Invalid Ballots","Home Voting", "Absentee Voting","Putin's Result"))
```

## Task 3. Visualize multiple OLS regression

```{r}

library(ggplot2)

a<-ggplot(President2018_new) + 
  aes(x=Invalid, y=Putin_percent) +
  geom_point() +
  ylab("Percentage of votes for Putin")+
  xlab("Invalid votes (percentage)")+
  ggtitle("")+
  stat_smooth(method = "lm", se = T, col="red")
  theme_bw()

b<-ggplot(President2018_new) + 
  aes(x=Home_voting, y=Putin_percent) +
  geom_point() +
  ylab("Percentage of votes for Putin")+
  xlab("Home voting (percentage)")+
  ggtitle("")+
  stat_smooth(method = "lm", se = T, col="red")
theme_bw()
  
c<-ggplot(President2018_new) + 
  aes(x=Absentee_voting, y=Putin_percent) +
  geom_point() +
  ylab("Percentage of votes for Putin")+
  xlab("Absentees (percentage)")+
  ggtitle("")+
  stat_smooth(method = "lm", se = T, col="red")
theme_bw()  
  
library(cowplot)  
plot_grid(a,b,c, labels = c('A', 'B', 'C'), label_size = 12, nrow = 1)
```

## Task 4. Supplementary statistics

#### Calculate the standardized beta coefficients

```{r}

library(lm.beta)
lm.beta(regr_Zhirinovskii)

lm.beta(regr_Putin)
```

#### Calculate the confidence intervals for beta coefficients 

```{r}

confint(regr_Putin)

confint(regr_Putin, level=0.99)
confint(regr_Zhirinovskii, level=0.999)
confint(regr_Sobchak, level=0.90)
confint(regr_Sobchak, level=1.0)
```

#### Represent the CIs in the regression output using the `stargazer` package

```{r}

stargazer(regr_Putin, regr_Grudinin, regr_Zhirinovskii, regr_Sobchak, 
          type="html",
          model.numbers = FALSE,
          ci = TRUE,
          title="Table 1. Regression Results",
          dep.var.labels=c("Putin","Grudinin", "Zhirinovskii", "Sobchak"), 
          covariate.labels=c("Invalid ballots","Home voting","Absentee voting"),
          omit.stat = c("ser", "f"),
          out="Elections-2018_CI.html") 
```

## Practice. Federal parliamentary elections-2016

1\. Import the dataset `ENPG2016.csv`

```{r}

df = read_delim("Data/ENPG2016.csv", 
    delim = ";", escape_double = FALSE, col_types = cols(Turnout = col_number(), 
        ER = col_number(), KPRF = col_number(), 
        LDPR = col_number(), SR = col_number(), 
        KR = col_number(), Yabloko = col_number(), 
        RPPS = col_number(), Rodina = col_number(), 
        PR = col_number(), Zelenye = col_number(), 
        PNS = col_number(), 
        GP = col_number(), GS = col_number()), 
    trim_ws = TRUE)

attach(df)
```

2\. Create a variable summarizing the results of small parties: `Yabloko`, `RPPS`, `Rodina`, `Zelenye`, `PNS`, `GP`, and `GS`. Add this variable to the dataset.

3\. Transform all the variables (except for `Region`) to percentages (divide them by 100)

4\. Build 5 multiple OLS models:

1.  DV = `ER`, IVs = `Turnout`, `PR` (percent of protest (invalid) votes)

2.  DV = `KPRF`, IVs = `Turnout`, `PR` (percent of protest (invalid) votes)

3.  DV = `LDPR`, IVs = `Turnout`, `PR` (percent of protest (invalid) votes)

4.  DV = `SR`, IVs = `Turnout`, `PR` (percent of protest (invalid) votes)

5.  DV = `Small parties` (your name), IVs = `Turnout`, `PR` (percent of protest (invalid) votes)

5\. Use the `stargazer` package to get a regression table for all five models. Include **confidence intervals** for beta coefficients into the table. Do not include **F-statistic** and **standard errors** in the table

6\. Calculate standardized beta coefficients in the first model (DV: `ER`)

7\. Build a graph unifying 5 scatterplots showing the dependence of the results of all the parties (including the sum for small parties) on turnout. All scatterplots should have regression trends of any color

```{r}
# Load required packages
library(dplyr)
library(stargazer)

# Create a variable summarizing the results of small parties
small_parties <- c("Yabloko", "RPPS", "Rodina", "Zelenye", "PNS", "GP", "GS")

df$`Small parties 2` = df$Yabloko+df$RPPS+df$Rodina
df <- df %>%
  mutate(`Small parties` = rowSums(select(., all_of(small_parties))))

# Transform variables to percentages
#enpg[, -1] <- enpg[, -1]/100

# Model 1: DV = ER
model1 <- lm(ER ~ Turnout + PR, data = df)
beta1 <- round(coef(model1)[-1], 3)

# Model 2: DV = KPRF
model2 <- lm(KPRF ~ Turnout + PR, data = df)
beta2 <- round(coef(model2)[-1], 3)

# Model 3: DV = LDPR
model3 <- lm(LDPR ~ Turnout + PR, data = df)
beta3 <- round(coef(model3)[-1], 3)

# Model 4: DV = SR
model4 <- lm(SR ~ Turnout + PR, data = df)
beta4 <- round(coef(model4)[-1], 3)

# Model 5: DV = Small parties
model5 <- lm(`Small parties` ~ Turnout + PR, data = df)
beta5 <- round(coef(model5)[-1], 3)

```
```{r}
# Calculate standardized beta coefficients for model 1
lm.beta(model1)
```
```{r}
confint(model1, level=0.99)
```


```{r}


stargazer(model1, model2, model3, model4, model5, 
          type="html",
          model.numbers = FALSE,
          ci = TRUE,
          title="Table 1. Regression Results",
          dep.var.labels=c("ER", "KPRF", "LDPR", "SR", "Small Parties"),
          covariate.labels=c("Turnout", "PR"),
          omit.stat = c("ser", "f"),
          out="Elections-2018_CI.html") 

```

```{r}
# Create scatterplot with regression trends
library(ggplot2)
library(tidyr)
df_long <- df %>% 
  select(-Region) %>% 
  pivot_longer(cols = -c(Turnout, PR), names_to = "Party", values_to = "Result")
ggplot(df_long, aes(x = Turnout, y = Result, color = Party)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  labs(title = "Results of All Parties vs Turnout", x = "Turnout", y = "Results")
```

