---
title: "Seminar 1"
author: "Aleksei Sorbale"
date: "2023-01-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**In this section you can leave comments/description to your operations if necessary**

Another option is to use the sign \# to leave comments

```{r}
### R as calculator. Mathematical symbols: +, -, *, /, ^

1+1
2-1
4/2
4^2
```

```{r}
### R as calculator. Mathematical functions: sqrt(), sum(), log(), log10(), log2(), log(x, base = y)

sqrt(121)
sum(12,13,14,15)
log(10)
log10(100)
log(1, base=10)
```

**Help call commands** if you forget something: *help( )*, *?*

```{r}
help("cor")
```


**Assignment operators**: \<-, =

Methods for **manual data entry** in R: function *c( )*
```{r}
digit <- c(1, 2, 3)
digit
```

# Task 1

Calculate ENP for the 2011 Duma elections using the formula by G.V.Golosov (2011)

```{r}
# First option
index_2011<-c(0.4931,0.1919,0.1325,0.1168,0.0343,0.0097,0.006)
sum(index_2011/(index_2011+max(index_2011)^2-index_2011^2))

# Second option
sum_index_2011<-0
for(i in index_2011)#for...in expression loop
	{sum_index_2011<-(i/(i+max(index_2011)^2-i^2))+sum_index_2011}
sum_index_2011
```

```{r}
getwd()# get the current working directory
setwd()# set the new working directory
```

# Task 2

[Creating and presenting tables]{.underline}: functions *data.frame( )*, *colnames( )*, *rownames( )*

```{r}
data_1<-c(1:5)
data_2<-c(6:10)
table_1<-data.frame(data_1,data_2)
colnames(table_1)<-c("Group 1", "Group 2")#give names to table columns 
rownames(table_1)<-c("Digit 1", "Digit 2", "Digit 3", "Digit 4", "Digit 5")#give names to table rows
table_1
```

# Practice
```{r}
data_Moscow<-c("Moscow", "CFD", 12500)
data_SPb<-c("St. Petersburg", "NWFD", 5600)
data_Kazan<-c("Kazan", "VFD", 1243)
data_Volga<-c("Volgograd", "SFD", 1013)
data_Nov<-c("N. Novgorod", "VFD", 1257)
data_Vlad<-c("Vladivostok", "FEFD", 605)
table_2<-data.frame(data_Moscow,data_SPb,data_Kazan,data_Volga,data_Nov,data_Vlad)
#colnames(table_1)<-c("Group 1", "Group 2")#give names to table columns 
rownames(table_2)<-c("City", "District", "Population")#give names to table rows
table_2
```


```{r}
data_cities<-c("Moscow", "St. Petersburg", "Kazan", "Volgograd", "N. Novgorod", "Vladivostok")
data_disctricts<-c("CFD", "NWFD", "VFD", "SFD", "VFD", "FEFD")
data_populations<-c(12500, 5600, 1243, 1013, 1257, 605)
table_3<-data.frame(data_cities,data_disctricts,data_populations)
colnames(table_3)<-c("City", "District", "Population")
table_3
```

Create a [table with Russian cities]{.underline}

|                |        |                |       |           |             |             |
|-----------|:---------:|:-----------:|:---------:|:---------:|:----------:|:----------:|
| **City**       | Moscow | St. Petersburg | Kazan | Volgograd | N. Novgorod | Vladivostok |
| **District**   |  CFD   |      NWFD      |  VFD  |    SFD    |     VFD     |    FEFD     |
| **Population** | 12500  |      5600      | 1243  |   1013    |    1257     |     605     |

```{r}
### Saving scripts and opening saved scripts
savehistory("Seminar_1")
q("no")

### Remove all objects from the current workspace
rm(list = ls())
```