---
title: "Seminar 2"
author: "Aleksei Sorbale"
date: "2023-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Task 1. Recall a table about the cities**

```{r}
city <- c("Moscow", "St.Petersburg", "Kazan", "Volgograd", "N.Novgorod", "Vladivostok")
district <- c("CFD", "NWFD", "VFD", "SFD", "VFD", "FEFD")
number <- c(12500, 5600, 1243, 1013, 1257, 605)
Russian_cities <- data.frame(City = city, District = district, Population = number)#Unification of objects into one table 
Russian_cities
```

**Basic extraction**

```{r}
Russian_cities$District#with $, ["name of component"] or[[number of component]] we can extract the individual components of the tables to perform the necessary calculations
Russian_cities$Population
Russian_cities["Population"]
Russian_cities$Population[4]#Extract the 4th item from the "Population" column
Russian_cities$Population[1:3]#Extract items 1-3 from the "Population" column
Russian_cities$City[Russian_cities$Population > 10000]#Extract the name of the city with a population value greater than 10 000
Russian_cities$City[Russian_cities$District == "VFD"]
Russian_cities[Russian_cities$District == "VFD" & Russian_cities$Population > 1000,]#setting two conditions at once: for the district and for the population size

```

## **Task 2. Importing data into R**

```{r}
### Import data into R from file format .csv: read.csv("D:/Way to file/File name.csv", sep=';')
Democracy<-read.csv("C:/Users/Alex/OneDrive/Документы/0_HSE_study/колы/2/Data/democracy_AER.csv", sep=',')#the same can be done with .dta, .spss, etc.
### Import data into R from file format .xlsx
Democracy[Democracy$country_name == "Pakistan",]
```
```{r}
Chechnya2016<-read.csv("C:/Users/Alex/OneDrive/Документы/0_HSE_study/колы/2/Data/Chechnya2016.csv",sep=';', header=TRUE, stringsAsFactors=FALSE, fileEncoding="latin1")
Chechnya2016
```

**"Cleaning" the data**

Download the data from Country and Territory Ratings and Statuses, 1973-2018

```{r}
Freedom<-read.csv("C:/Users/Alex/OneDrive/Документы/0_HSE_study/колы/2/Data/Country_and_Territory_Ratings_and_Statuses_FIW1973-2019.csv", sep=';', header=TRUE, stringsAsFactors=FALSE, fileEncoding="latin1")
Freedom
Freedom_new<-Freedom[c("Number.of.NF.Countries", "Total.Countries", "Number.of.PF.Countries")]

Freedom_good<-na.omit(Freedom_new)# na.omit = remove all NAs from the database
```

## **Task 3. Elections in France-2017**

```{r}
France<-read.csv("C:/Users/Alex/OneDrive/Документы/0_HSE_study/колы/2/Data/French_Presidential_Election_2017.csv", sep=';', header=TRUE, stringsAsFactors=FALSE, fileEncoding="latin1")
summary(France)#all the information about dataset
summary(France$Voters)#all the information about the concrete variable in the dataset
```

**Descriptive statistics with table1**

```{r}
library(table1)
France_table<-table1(~ Sex + Constituency + Abstentions + Registered, data=France)
France_table
```

**Items of descriptive statistics**

```{r}
Happiness<-read.csv("C:/Users/Alex/OneDrive/Документы/0_HSE_study/колы/2/Data/happiness.csv", sep=';')
max(Happiness$happy)
min(Happiness$GINI)
mean(Happiness$god_imp)
quantile(Happiness$happy)
sd(Happiness$happy)
hist(Happiness$GINI, main = "Histogram of GINI index in the UN states", 
     xlab = "GINI index")#histogram of the normality of distribution
```

## **Practice. Public opinion in 2012**

1.  Import the dataset "data2012_mneniye.csv"
2.  Get the descriptive statistics for the dataset: min and max for variables, sd for variables, mean values, quartiles (can be done with one or several functions)
3.  Extract only the people of 50+ years who trust Putin (Trust_Putin == 1)
4.  Clean the dataset: leave only the variables "Age", "Satisfaction", "Education", "Region". Remove all NAs
5.  Create a histogram with the title and labels (any) for variable "Education"
6.  Create a scatterplot with the title and labels (any) for variable "Protest"

```{r}
Mnenie<-read.csv("C:/Users/Alex/OneDrive/Документы/0_HSE_study/колы/2/Data/data2012_mneniye.csv", sep=';')
summary(Mnenie)
Putin_old<-Mnenie[Mnenie$Trust_Putin == 1 & Mnenie$Age > 50,]
Putin_old
Putin_old_clear<-na.omit(Putin_old)
Putin_old_clear_filtered<-Putin_old_clear[c('Age', 'Satisfaction', 'Education', 'Region')]
Putin_old_clear_filtered

hist(Putin_old_clear_filtered$Education, main = "Education of 50+ Putin Supporters", 
     xlab = "Education")

plot(Mnenie$Age, Mnenie$Region, main="Scatterplot Example",
   xlab="Age", ylab="Region")
```
