---
title: "Untitled"
output: html_document
date: "2023-03-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
ESS10 <- read_sav("~/0_teaching/2/ESS10.sav")
```

Step 0 - clear the dataset, leave only important things

```{r}
library(dplyr)

greece <- filter(ESS10, ESS10$cntry == "GR")
```

Let's describe relationships between the following pairs of variables: 

- `polintr` and `vote` 

I expect to find out if there is a relationship between the level of political interest (polintr) and whether individuals voted during last national elections (vote).

```{r}
greece_2 <- greece %>% select(polintr, vote)
greece_2 <- na.omit(greece_2)
greece_2
```
```{r}
greece_2$polintr <- as.numeric(greece_2$polintr)
greece_2$vote <- as.numeric(greece_2$vote)
greece_2
```

Part I. Chi-squared Test (2 points)
1) The correct choice of variables. A plot with the two variables involved (0.5 points)

```{r}
library(ggplot2)

# Convert the variables to factors
greece_2$polintr <- factor(greece_2$polintr)
greece_2$vote <- factor(greece_2$vote)

# Create a table with the counts for each combination of polintr and vote
table_data <- table(greece_2$polintr, greece_2$vote)

# Convert the table to a data frame
table_df <- as.data.frame.matrix(table_data)

# Add row names as a variable
table_df$polintr <- rownames(table_df)

# Reshape the data from wide to long format
table_long <- reshape2::melt(table_df, id.vars = "polintr")

# Create the stacked bar chart
ggplot(table_long, aes(x = polintr, y = value, fill = variable)) + 
  geom_bar(stat = "identity") + 
  labs(x = "Political Interest", y = "Count", fill = "Vote")

```
2) The null hypothesis is spelled out, and you make conclusions as table(flowers)
to how the results relate to it (0.5)

`Vote` Categories
1	Yes
2	No
3	Not eligible to vote

`polintr`	Category
1	Very interested
2	Quite interested
3	Hardly interested
4	Not at all interested


Null hypothesis (H0): ________________________________________
Alternative hypothesis (HA): ___________________________________

```{r}
# Perform chi-squared test of independence
chisq_res <- chisq.test(table_data)

# Print the test result
chisq_res
```
results: __________________________________________

```{r}
library(gmodels)
CrossTable(table_data, expected=T)
```

3) You have checked all the assumptions of the chi-square test and they are matched. You have run and correctly interpreted the chi-square test, analysing the standardized residuals (1)

we _____ reject H0

standardized residuals: ______________________________________


Part II. The t-test (2.5 points)
4) The correct choice of variables, a plot with these variables (0.5)
```{r}
greece_3 <- greece %>% select(netustm, vote)
greece_3 <- na.omit(greece_3)
greece_3$netustm <- as.numeric(greece_3$netustm)
greece_3$vote <- as.numeric(greece_3$vote)
greece_3
```


netustm - internet use in minutes
vote - national elections

```{r}


# Create a vector for each vote category (1, 2, 3)
vote_1 <- subset(greece_3, vote == 1)$netustm
vote_2 <- subset(greece_3, vote == 2)$netustm
vote_3 <- subset(greece_3, vote == 3)$netustm #We will not use it

```

```{r}
ggplot() + labs (title = "Internet use in minutes vs Voting", x="Did people vote on last national elections?", y="") +
  geom_boxplot(aes(x='Yes', y=vote_1), fill="tomato1") + 
  geom_boxplot(aes(x='No', y=vote_2), fill="purple4") + 
  theme_bw()
```
5) You have checked the normality assumption for the t-test in 2 different ways (QQ plots / histogram / skew and kurtosis) (0.5)

```{r}
shapiro.test(vote_1)
shapiro.test(vote_2)
var.test(vote_1, vote_2)
```
```{r}
# QQ plot for vote_1
qqnorm(vote_1)
qqline(vote_1)

# Histogram for vote_1
hist(vote_1)

```
```{r}
# QQ plot for vote_2
qqnorm(vote_2)
qqline(vote_2)

# Histogram for vote_2
hist(vote_2)

```

```{r}
library(moments)

# Calculate skewness and kurtosis for vote_1
skewness(vote_1)
kurtosis(vote_1)

# Calculate skewness and kurtosis for vote_2
skewness(vote_2)
kurtosis(vote_2)

```
normality: _____________________________
variances: ________________________________
parametric: ___________________________

6) The null hypothesis is spelled out, and you make conclusions as to how the results relate to it. You have applied the correct t-test formula and interpreted the result correctly. If the result is statistically significant, the effect size is reported (1)

Null hypothesis: ____________________________________________________

Alternative hypothesis: _______________________________________________________

```{r}
t.test(vote_1, vote_2, var.equal = TRUE)
```
result: _______________________________________

7) You have double-checked your results with a non-parametric test (0.5)

```{r}
wilcox.test(vote_1, vote_2, alternative = "two.sided")
```
result: __________________________________________
