---
title: "Untitled"
author: "Diana Piskareva"
date: "2023-03-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r warning = FALSE}
library(haven)
library(ggplot2)
library(gplots)
library(dplyr)
library(vcd)
library(kableExtra)

```
Thus, in order to perform the necessary manipulations with the data, we downloaded the date ESS 2020
```{r warning = FALSE}
ESS10 <- read_sav("~/0_teaching/2/ESS10.sav")
ESS10
```

Part I. Chi-squared Test (2 points)
1) The correct choice of variables. A plot with the two variables involved (0.5 points)
2) The null hypothesis is spelled out, and you make conclusions as table(flowers)
to how the results relate to it (0.5)
3) You have checked all the assumptions of the chi-square test and they are matched. You have run and correctly interpreted the chi-square test, analysing the standardized residuals (1)

#I want to consider two categorical variables for the chi-squared test: how people vote and how people are interested in politics (polintr), that is, my goal is to see if there is any relationship between them within Greece  
```{r warning = FALSE}

# table(ESS6$cntry)
gr <- filter(ESS10, ESS10$cntry == "GR")
head(gr)

```

```{r warning = FALSE}
grS <- gr %>% 
  select(polintr,vote)


```
```{r warning = FALSE}
grS = grS%>%
  mutate(polintr = case_when(polintr=="Very interested" ~ "4",polintr=="Quite interested" ~ "3",polintr=="Hardly interested" ~ "2", polintr=="Not at all interested" ~ "1"))

```

```{r setup, include=FALSE}
#H0: the variables are independent, there is no relationship between vote and polintr. Knowing the value of one variable does not help to predict the value of the other variable

#H1: the variables are dependent, there is a relationship between the vote and polintr. Knowing the value of one variable helps to predict the value of the other variable

grS$polintr <- as.numeric(as.character(grS$polintr))

```

```{r setup, include=FALSE}

counts <- table(grS$vote, grS$polintr)
barplot(counts, main="distribution political interests and vote",
  xlab="Political interests", col=c("pink","lightblue","lightgreen"),
  legend = rownames(counts))
barplot()
```

```{r setup, include=FALSE}

ggplot(grS, aes(x = factor(vote), fill = factor(polintr))) +
  geom_bar(position = "stack") +
  labs(x = "Vote", y = "", title = "Joint Distribution of political interest and vote", fill = "Political interests")
ggplot()
```


```{r setup, include=FALSE}


mosaic(~ vote + polintr ,
  direction = c("v", "h"),
  data = grS,
  shade = TRUE
)
mosaic()

```


Part II. The t-test (2.5 points)
4) The correct choice of variables, a plot with these variables (0.5)
5) You have checked the normality assumption for the t-test in 2 different ways (QQ plots / histogram / skew and kurtosis) (0.5)
6) The null hypothesis is spelled out, and you make conclusions as to how the results relate to it. You have applied the correct t-test formula and interpreted the result correctly. If the result is statistically significant, the effect size is reported (1)
7) You have double-checked your results with a non-parametric test (0.5)


```{r setup, include=FALSE}
grN <- gr %>% 
  select(nwspol, vote) %>% 
    filter(vote != 3) %>% 
  filter(vote != 7) %>% 
  filter(vote != 8) %>% 
  filter(vote != 9) %>% 
  filter(nwspol !=7777) %>% 
    filter(nwspol !=8888) %>% 
    filter(nwspol !=9999)  
```


```{r setup, include=FALSE}
ggqqplot(grN, x = "weight")




```



```{r setup, include=FALSE}


```

```{r setup, include=FALSE}
```

```{r setup, include=FALSE}
```

```{r setup, include=FALSE}
```

