---
title: "Seminar 8"
author: "Aleksei Sorbale"
date: "2023-03-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Paired regression: Children & Parents Height**

```{r}
#install.packages("HistData")
library(HistData)
attach(Galton)
```

#### Change the scale

Assign the height of children and the height of parents from Galton dataset to the `child_new` and `parent_new` objects

Multiplication by 2.54 is made to bring the height values into compliance with the metric system. The original values are in inches: [1 inch = 2.54 centimeters]{.underline}

```{r}
child_new<-Galton$child*2.54 
parent_new<-Galton$parent*2.54
```

**Paired regression**

```{r}
galton_regr<-lm(child_new~parent_new)
summary(galton_regr)
```

**Visualization of the relationship** **with base R**

```{r}
plot(parent_new, child_new, main = "", ylab ="", xlab = "")
title(main = "Dependence of the height of children on the height of parents", ylab="Children height", xlab="Parents height")
abline(galton_regr, col = "blue")#regression line (trend)
```

## Paired regression: Satisfaction with governmental policy & Age

**Option 1: with NAs**

```{r}
library(readr)
data <- read_delim("~/0_HSE_study/колы/8/Data/data2012_mneniye.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
attach(data)
```

```{r}
data_regr_1<-lm(Satisfaction~Age)
summary(data_regr_1)
```

**Option 2: without NAs**

```{r}
data_new<-na.omit(data)
attach(data_new)

data_regr_2<-lm(Satisfaction~Age)
summary(data_regr_2)
```

## Paired regression: Political stability & Government effectiveness

```{r}
World <- read_delim("~/0_HSE_study/колы/8/Data/World_data.csv", 
    delim = ",", escape_double = FALSE, trim_ws = TRUE)
attach(World)
```

```{r}
regr_World<-lm(Political_Stability~Government_Effectiveness)
summary(regr_World)
```

Calculate a new variable `Democracy Sustainability Index` and put it into the dataset. Democracy Sustainability Index is the product of the following formula: $$\dfrac{Political\_Rights + Civil\_Liberties}{1-Government\_Effectiveness^2}$$

**Put this DSI variable into the original dataset**:

```{r}
World$Democracy_Index = (Political_Rights+Civil_Liberties)/1-Government_Effectiveness^2
```

**Remove the variables used for Democracy Sustainability Index calculation from the dataset**:

*dplyr* option

```{r}
World = dplyr::select(World, -Political_Rights, -Civil_Liberties, -Government_Effectiveness)
```

*Base R* option

```{r}
World = World[,-c(4,8,9)]
```

## Paired regression: Democracy Stability Index & Rule of law

```{r}
attach(World)

regr_World2<-lm(Democracy_Index~Rule_of_Law)
summary(regr_World2)
```

**Visualization of the relationship** **with `ggplot2`**

```{r}
library(ggplot2)
library(ggthemes)
ggplot(World) + 
  aes(x=Democracy_Index, y=Rule_of_Law) +
  geom_point() +
  ylab("Rule of law index")+
  xlab("Democracy index")+
  ggtitle("Dependence of the Democracy Index from the Rule of Law")+
  stat_smooth(method = "lm", col="red")+
  theme_bw()

```

## Practice: 2018 presidential elections in Russia

1.  Import the dataset `Presidential_elections_2018.csv`

```{r}
library(readr)
Presidential_elections_2018 <- read_delim("~/0_HSE_study/колы/8/Data/Presidential_elections_2018.csv", 
    delim = ";", escape_double = FALSE, col_types = cols(Number_of_voters = col_number(), 
        Absentee_Ballots = col_number(), 
        Station_Ballots = col_number(), Home_Ballots = col_number(), 
        Home_Box_Ballots = col_number(), 
        Station_Box_Ballots = col_number(), 
        Invalid_votes = col_number(), Valid_votes = col_number(), 
        Baburin_votes = col_number(), Grudinin_votes = col_number(), 
        Zhirinovskii_votes = col_number(), 
        Putin_votes = col_number(), Sobchak_votes = col_number(), 
        Suraikin_votes = col_number(), Titov_votes = col_number(), 
        Yavlinskii_votes = col_number()), 
    trim_ws = TRUE)
head(Presidential_elections_2018)
```

2.  Calculate the `Turnout` variable. The formula for calculation is as follows:

$$
\dfrac{Station\_Ballots + Home\_Ballots}{Number\_of\_voters}
$$
```{r}
Presidential_elections_2018$Turnout <- (Presidential_elections_2018$Station_Ballots + Presidential_elections_2018$Home_Ballots) / Presidential_elections_2018$Number_of_voters
```

3.  Add the `Turnout` variable to the dataset
4.  Filter the dataset so that it contains only the following variables: `Region`, `Turnout` (the variable created at step 2), `Number_of_voters`, `Home_Ballots`, `Invalid_votes`, `Putin_percent`

```{r}
data_filtered <- subset(Presidential_elections_2018, select = c("Region", "Turnout", "Number_of_voters", "Home_Ballots", "Invalid_votes", "Putin_percent"))
head(data_filtered)
```

5.  Build a correlation matrix (`cor()` function) for the variables included in the dataset (except for `Region`).

**NB!** Before proceeding to the matrix building, unify the 5 variables of interest into a `data.frame`

```{r}
data_cor <- data_filtered[, 2:6]
cor_matrix <- cor(data_cor)
cor_matrix
```


6.  Conduct paired OLS-regression for the pair of variables, which correlation coefficient is the **SMALLEST BY MODULE** according to the correlation matrix

```{r}
regression <- lm(Turnout ~ Putin_percent, data = data_filtered)
summary(regression)
```

7.  Build a paired OLS-regression plot for the variables you have chosen, give it a name and captions on the axes, draw a regression trend

```{r}
library(ggplot2)
ggplot(data_filtered, aes(x = Putin_percent, y = Turnout)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Percentage of Votes for Putin") +
  ylab("Turnout") +
  ggtitle("Relationship between Turnout and Votes for Putin")

```

