---
title: "Untitled"
output: html_document
date: "2023-05-10"
---

1. Import the dataset Karelia2016.csv.

```{r}
library(readr)
Karelia2016 <- read_delim("~/0_programming/0_prog/0_HSE_study/колы/11/Data/Karelia2016.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
Karelia2016
```
2. Calculate the Turnout variable. 
Tip 1: Turnout variable formula: (Com_Ballots + Home_Ballots)/Voters. 

```{r}
Karelia2016$Turnout <- (Karelia2016$Com_Ballots + Karelia2016$Home_Ballots)/Karelia2016$Voters
Karelia2016
```
3. Calculate the percent of invalid ballots and percent of people, who voted at home (Invalid and Home_Ballots variables are needed here). 

```{r}
Karelia2016$Invalid_p <- Karelia2016$Invalid/Karelia2016$Voters
Karelia2016$Home_Ballots_p <- Karelia2016$Home_Ballots/(Karelia2016$Com_Ballots + Karelia2016$Home_Ballots)
Karelia2016
```
5. Filter the dataset so that only the following variables remain:

• United_Russia: percent of votes for United Russia

• Home_Ballots (or your name): percent of people, who voted at home

• Invalid (or your name): percent of invalid ballots

• Turnout: turnout on the elections in Karelia
```{r}
library(dplyr)

Karelia <- dplyr::select(Karelia2016,United_Russia,Home_Ballots_p, Invalid_p, Turnout)
Karelia
```
6. Round the values in all four variables to 3 decimal places (thousandth).
```{r}
Karelia <- round(Karelia, digits = 3)
Karelia
```
7. Build the following OLS model: DV = United_Russia, IVs = Home_Ballots (or your name), Invalid (or your name), Turnout.
```{r}
model <- lm(United_Russia ~ Home_Ballots_p + Invalid_p + Turnout, data = Karelia)
summary(model)
```
8. Check the model for outliers. Give a brief interpretation: are there any outliers in the model, if yes, where are they situated (which line(s))?

```{r}
library(car)
outlierTest(model)

### Outliers in the model - 100 (Bonferroni p < 0.05)
```

9. Check the model for influential observations. Give a brief interpretation: are there any influential observations in the model, if yes, where are they situated (which line(s))? If the model contains influential observations, delete them and run the model without them!

```{r}
plot(model, which = 4, cook.levels = 1)#"cook.levels = 1" - identify the default Cook's distance, "which" - number of plot in a series
abline(h=1, lty=2, col="red")

### No there are no influential observations (no observation crosses the cook distance)
```


10. Check the model for heteroscedasticity.

a. Build a spreadLevel plot;

Interpret the plot outlook: which element(s) and their positioning can be used in order to make an assumption about the presence/absence of the problem?

b. Run the test;

c. Indicate whether the problem is present in the model. Explain, which values and/or sections of the test output drove you to the respective conclusion;

d. If the problem does exist, fix it with the respective tool.

```{r}
spreadLevelPlot(model)

# The blue dashed trendline is going up (**not being horizontal**) and pink reference line is varying (**not being flat**) so we can assume the problem of non-constant DV variance is present (aka heteroscedasticity)
ncvTest(model)

# p < 0.005 -> heteroscedasticity is present
```
```{r}
library(sandwich)
library(lmtest)
model_fixed <- coeftest(model, vcovHC(model))
model_fixed
```


11. Use the stargazer package to draw the table with regression output. Do not include F- statistic in the table. (for this task use the final version of the corrected model)

```{r}
library(stargazer)

stargazer(model_fixed, 
          type="html",
          model.numbers = FALSE,
          title="Table 1. Regression Results",
          dep.var.labels=c("United Russia"), 
          covariate.labels=c("Home voting","Invalid ballots","Turnout"),
          omit.stat = c("f"),
          out="Elections_Karelia.html") 
```

