---
title: "Untitled"
output: html_document
date: "2023-03-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`sort`

Say we want to rank the states from least to most gun murders. The function sort sorts
a vector in increasing order. We can therefore see the largest number of gun murders by
typing:

```{r}
#install.packages("dslabs")
library(dslabs)
data(murders)
sort(murders$total)
```
```{r}
head(murders)
```

However, this does not give us information about which states have which murder totals.
For example, we don’t know which state had 1257.

`order`

The function order is closer to what we want. It takes a vector as input and returns the
vector of indexes that sorts the input vector. This may sound confusing so let’s look at a
simple example. We can create a vector and sort it:

```{r}
x <- c(31, 4, 15, 92, 65)
sort(x)
```
Rather than sort the input vector, the function order returns the index that sorts input
vector:

```{r}
index <- order(x)
x[index]
```
This is the same output as that returned by `sort(x)`. If we look at this index, we see why
it works:

```{r}
x
order(x)
```
How does this help us order the states by murders? First, remember that the entries of
vectors you access with `$` follow the same order as the rows in the table. For example, these
two vectors containing state names and abbreviations, respectively, are matched by their
order:

```{r}
murders$state[1:6]
murders$abb[1:6]
```
```{r}
ind <- order(murders$total)
murders$abb[ind]
murders$state[ind]
```
`max` and `which.max`
If we are only interested in the entry with the largest value, we can use max for the value:

```{r}
max(murders$total)
```
and `which.max` for the index of the largest value:

```{r}
which.max(murders$total)

murders$state[which.max(murders$total)]
```
For the minimum, we can use `min` and `which.min` in the same way.

`rank`
Although not as frequently used as `order` and `sort`, the function `rank` is also related to
order and can be useful. For any given vector it returns a vector with the `rank` of the first
entry, second entry, etc., of the input vector. Here is a simple example:

```{r}
x <- c(31, 4, 15, 92, 65)
rank(x)
```
```{r}
df <- data.frame(original = c(31, 4, 15, 92, 65))
df$sort <- sort(df$original)
df$order <- order(df$original)
df$rank <- rank(df$original)
df
```
```{r}
a <- c(4, 6, 7, 56)

sort(a, decreasing = TRUE)
```

Common mistakes ("recycling"):

```{r}
x <- c(1,2,3)
y <- c(10, 20, 30, 40, 50, 60, 70)
x+y
```
# Practice

1. Use the `$` operator to access the **population size** data and store it as the object `pop`. Then
use the `sort` function to redefine **pop** so that it is sorted. Finally, use the `[` operator to
report the **smallest** population size.

2. Now instead of the **smallest population size**, find the **index of the entry with the smallest population size**. 
Hint: use `order` instead of `sort`.

3. We can actually perform the same operation as in the previous exercise using the function
`which.min`. Write one line of code that does this.

4. Now we know how small the smallest state is and we know which row represents it. **Which state is it?** 
Define a variable `states` to be the state names from the murders data frame.
**Report the name of the state with the smallest population.**

5. You can create a data frame using the data.frame function. Here is a quick example:

```{r}
temp <- c(35, 88, 42, 84, 81, 30)
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro","San Juan", "Toronto")
city_temps <- data.frame(name = city, temperature = temp)
```

Use the `rank` function to determine the population rank of each state from smallest population size to biggest. 
Save these `ranks` in an object called `ranks`, then create a data frame
with the state name and its rank. Call the data frame `my_df`.

6. Repeat the previous exercise, but this time order `my_df` so that the states are ordered
**from least populous to most populous**. Hint: create an object ind that stores the indexes
needed to order the population values. Then use the bracket operator `[` to re-order each
column in the data frame.

7. Order `murders` dataset as well **from least populous to most populous**

8. We want to create a new variable called `murder_rate`, which is the number of murders per 100,000
people. Use the `$` operator to access the number of murders `total` then divide murders by `population` from `murders` dataset, multiply by 100,000, and save the result as a new column in the `my_df` data frame.

9. Create a simple visualisation of `murder_rate` variable using `plot()` function

10. What state has the **highest** `murder_rate`?
