---
title: "Untitled"
output: html_document
date: "2023-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dslabs)
data(murders)
murders
```

# Practice

1. Use the `$` operator to access the **population size** data and store it as the object pop. Then
use the `sort` function to redefine **pop** so that it is sorted. Finally, use the `[` operator to
report the **smallest** population size.

```{r}
pop <- murders$population
sort(pop)[1]
```

2. Now instead of the **smallest population size**, find the **index of the entry with the smallest population size**. 
Hint: use `order` instead of `sort`.

```{r}
order(pop)[1]
```
3. We can actually perform the same operation as in the previous exercise using the function
`which.min`. Write one line of code that does this.

```{r}
which.min(pop)
```


4. Now we know how small the smallest state is and we know which row represents it. **Which state is it?** 
Define a variable `states` to be the state names from the murders data frame.
**Report the name of the state with the smallest population.**

```{r}
i <- which.min(pop)
murders$state[i]
```


5. You can create a data frame using the data.frame function. Here is a quick example:

```{r}
temp <- c(35, 88, 42, 84, 81, 30)
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro","San Juan", "Toronto")
city_temps <- data.frame(name = city, temperature = temp)
```

Use the `rank` function to determine the population rank of each state from smallest population size to biggest. 
Save these `ranks` in an object called `ranks`, then create a data frame
with the state name and its rank. Call the data frame `my_df`.

```{r}
ranks <- rank(murders$population)
my_df <- data.frame(state = murders$state, ranks = ranks)
my_df
```


6. Repeat the previous exercise, but this time order `my_df` so that the states are ordered
**from least populous to most populous**. Hint: create an object ind that stores the indexes
needed to order the population values. Then use the bracket operator `[` to re-order each
column in the data frame.

```{r}
ind <- order(murders$population)
my_df <- my_df[ind, ]
my_df
```
7. Order `murders` dataset as well **from least populous to most populous**

```{r}
murders <- murders[ind,]
murders
```


8. We want to create a new variable called `murder_rate`, which is the number of murders per 100,000
people. Use the `$` operator to access the number of murders `total` then divide murders by `population` from `murders` dataset, multiply by 100,000, and save the result as a new column in the `my_df` data frame.

```{r}
my_df$murder_rate <- murders$total / murders$population * 100000
my_df
```
9. Create a simple visualisation of `murder_rate` variable using `plot()` function
```{r}
plot(my_df$murder_rate)
```
10. What state has the highest `murder_rate`?

```{r}
ii <- which.max(my_df$murder_rate)
my_df$state[ii]
```

