---
title: "Untitled"
output: html_document
date: "2023-03-01"
---
```{r}
library(readr)
Pol_Stab <- read_csv("~/0_HSE_study/колы/7/Data/Pol_Stab.csv")
Gov_eff <- read_csv("~/0_HSE_study/колы/7/Data/Gov_eff.csv")
Rule_of_law <- read_csv("~/0_HSE_study/колы/7/Data/Rule_of_law.csv")
head(Pol_Stab)

### I did this task before Aleksey Borisovich sent the dataset and downloaded all of them myself. They downloaded as three different datasets therefore i had to unite them manually. I spoke about it with Aleksey Borisovich and he was okay with it.
```
```{r}
summary(Pol_Stab) ### There are a lot of duplicate values for some reason, so i am filtering the data leaving only unique ones
Pol <- unique(Pol_Stab)
summary(Pol)
names(Pol) <- c("Country", "Political Stability") ### Renaming the column
head(Pol)
```
```{r}
library(dplyr)
Pol_asc <- arrange(Pol, Country) ### Making an ascending order 
Pol_asc
```

```{r}
Gov <- unique(Gov_eff) ### Doing the same thing with other values
names(Gov) <- c("Country", "Government Effectiveness")
Gov_asc <- arrange(Gov, Country)
Gov_asc
```
```{r}
Law <- unique(Rule_of_law)
names(Law) <- c("Country", "Rule of Law")
Law_asc <- arrange(Law, Country)
Law_asc
```
```{r}
WGI <- merge(Pol_asc, Gov_asc, by = "Country") %>%
                  merge(Law_asc, by = "Country")
WGI <- WGI %>% 
  mutate(Country = gsub("Türkiye", "Turkiye", Country))
WGI ### Merging into one dataset for these three values from WGI
```
```{r}
worldBank <- read_csv("~/0_HSE_study/колы/7/Data/WorldBankData.csv", 
    col_types = cols(`2020 [YR2020]` = col_number()))
wb_data_selected <- select(worldBank, 1, 3, 5) ## Leaving only important values
names(wb_data_selected) <- c("Country", "Category", "Value")
wb_data_selected <- na.omit(wb_data_selected)
wb_data_selected
```
```{r}
library(tidyr)

# Create separate columns for each variable
WB <- spread(wb_data_selected, key = Category, value = Value)

WB <- WB %>% 
  mutate(Country = gsub("Czechia", "Czech Republic", Country)) ## Countries are named different in different datasets
WB

```
```{r}
WGI_WB <- merge(WGI, WB, by = "Country") ## merging them
WGI_WB
```
```{r}
library(readxl)
Aggregate_Category_and_Subcategory_Scores_FIW_2003_2022 <- read_excel("~/0_HSE_study/колы/7/Data/Aggregate_Category_and_Subcategory_Scores_FIW_2003-2022.xlsx", 
    sheet = "FIW06-22")
FH_sel <- select(Aggregate_Category_and_Subcategory_Scores_FIW_2003_2022, 1, 2, 4, 13, 18)
FH_sel
```
```{r}
FH_sel_2020 <- FH_sel %>% filter(Edition == "2020") ### taking data only for 2020
FH_sel_2020_e <- FH_sel_2020 %>% filter(Region == "Europe" | Region == "Eurasia") ## Taking region europe and adding to them countrie that are not considered europe for some reason
FH_sel_2020_e <- FH_sel_2020_e %>% mutate(Country = gsub("Russia", "Russian Federation", Country))
FH_sel_2020_e <- FH_sel_2020_e %>% mutate(Country = gsub("Slovakia", "Slovak Republic", Country))
FH_sel_2020_e <- FH_sel_2020_e %>% mutate(Country = gsub("Turkey", "Turkiye", Country))
FH_sel_2020_selected <- select(FH_sel_2020_e, 1, 4, 5)
FH_sel_2020_selected
```
```{r}
All_data <- merge(WGI_WB, FH_sel_2020_selected, by = "Country")
All_data_cleared <- na.omit(All_data)
All_data_cleared 
colnames(All_data_cleared) <- c("Country", "Political Stability", "Government Effectiveness", "Rule of Law", "GDP per capita", "Population growth", "Political Rights", "Civil Liberties")
```
Well i guess I did the dataset......
Hopefully minor nations excluded are not very important

########
2. Implement the following paired correlations: (1) Political Stability – Government Effectiveness, (2) Political Stability – Rule of Law, (3) Political Stability – Political Rights, (4) Political Stability – Civil Liberties, (5) Political Stability – GDP per capita and (6) Political stability – Population growth. 

i. Before proceeding to the paired correlations, check the variables in each pair for parametricity. Use # for a short interpretation of the tests output for each pair: what correlation coefficient (Pearson or Spearman) should be calculated for the respective pair and why.
ii. Interpret the results of the correlation analysis in each of the pairs. What does the correlation coefficient mean for each pair of variables in terms of direction and strength of relationship? Can it be treated as significant (can the H0 for correlation test be rejected)? Give a brief comment for each pair with #

```{r}
#(1) Political Stability – Government Effectiveness
# Firstly we need to check the data for parametricity
shapiro.test(All_data_cleared$`Political Stability`) #p-value = 0.05009 > 0.05 - normally dist
shapiro.test(All_data_cleared$`Government Effectiveness`) #p-value = 0.05484 > 0.05 - normally dist
var.test(All_data_cleared$`Political Stability`, All_data_cleared$`Government Effectiveness`) #p-value = 0.2979 > 0.05 - hom var

### The data is parametric therefore we have to use pearson test

cor.test(All_data_cleared$`Political Stability`, All_data_cleared$`Rule of Law`, method = "pearson")#p-value = 4.393e-16

### The correlation is statistically significant (H0 can be rejected). It is positive and rather strong. cor = 0.8791252    
```
```{r}
#(2) Political Stability – Rule of Law
# Firstly we need to check the data for parametricity
shapiro.test(All_data_cleared$`Political Stability`) #p-value = 0.05009 > 0.05 - normally dist
shapiro.test(All_data_cleared$`Rule of Law`) #p-value = 0.01703 < 0.05 - not normally dist
var.test(All_data_cleared$`Political Stability`, All_data_cleared$`Rule of Law`) #p-value = 0.1269 > 0.05 - hom var

### The data is not parametric therefore we have to use spearman test

cor.test(All_data_cleared$`Political Stability`, All_data_cleared$`Rule of Law`, method = "spearman")#p-value < 2.2e-16

### The correlation is statistically significant (H0 can be rejected). It is positive and rather strong. cor = 0.8858696   
```
```{r}
#(3) Political Stability – Political Rights
# Firstly we need to check the data for parametricity
shapiro.test(All_data_cleared$`Political Stability`) #p-value = 0.05009 > 0.05 - normally dist
shapiro.test(All_data_cleared$`Political Rights`) #p-value = 2.041e-07 < 0.05 - not normally dist
var.test(All_data_cleared$`Political Stability`, All_data_cleared$`Political Rights`) #p-value < 2.2e-16 < 0.05 - not hom var

### The data is not parametric therefore we have to use spearman test

cor.test(All_data_cleared$`Political Stability`, All_data_cleared$`Political Rights`, method = "spearman")#p-value = 2.955e-09

### The correlation is statistically significant (H0 can be rejected). It is positive and rather strong. cor = 0.7392306   
```

```{r}
#(4) Political Stability – Civil Liberties
# Firstly we need to check the data for parametricity
shapiro.test(All_data_cleared$`Political Stability`) #p-value = 0.05009 > 0.05 - normally dist
shapiro.test(All_data_cleared$`Civil Liberties`) #p-value = 2.085e-06 < 0.05 - not normally dist
var.test(All_data_cleared$`Political Stability`, All_data_cleared$`Civil Liberties`) #p-value < 2.2e-16 < 0.05 - not hom var

### The data is not parametric therefore we have to use spearman test

cor.test(All_data_cleared$`Political Stability`, All_data_cleared$`Civil Liberties`, method = "spearman")#p-value = 6.662e-16

### The correlation is statistically significant (H0 can be rejected). It is positive and rather strong. cor = 0.8767242 
```

```{r}
#(5) Political Stability – GDP per capita
# Firstly we need to check the data for parametricity
shapiro.test(All_data_cleared$`Political Stability`) #p-value = 0.05009 > 0.05 - normally dist
shapiro.test(All_data_cleared$`GDP per capita`) #p-value = 5.674e-10 < 0.05 - not normally dist
var.test(All_data_cleared$`Political Stability`, All_data_cleared$`GDP per capita`) #p-value < 2.2e-16 < 0.05 - not hom var

### The data is not parametric therefore we have to use spearman test

cor.test(All_data_cleared$`Political Stability`, All_data_cleared$`GDP per capita`, method = "spearman")#p-value = 0.4871

### The correlation is not statistically significant (H0 cannot be rejected). It is positive and weak. cor = 0.1036078   
```
```{r}
#(6) Political stability – Population growth. 
# Firstly we need to check the data for parametricity
shapiro.test(All_data_cleared$`Political Stability`) #p-value = 0.05009 > 0.05 - normally dist
shapiro.test(All_data_cleared$`Population growth`) #p-value = 0.2532 < 0.05 - not normally dist
var.test(All_data_cleared$`Political Stability`, All_data_cleared$`Population growth`) #p-value = 0.7888 > 0.05 - hom var

### We proved that data is parametric therefore we have to use pearson test

cor.test(All_data_cleared$`Political Stability`, All_data_cleared$`Population growth`, method = "spearman")#p-value = 5.688e-05

### The correlation is statistically significant (H0 can be rejected). It is positive and rather strong. cor = 0.5602451  
```
```{r}
### We should delete country column to  make this work
all_data_new <- select(All_data_cleared, -1)
all_matrix <- cor(all_data_new)
all_matrix
```
```{r}
library(GGally)
ggpairs(all_data_new)
```


3. Create a correlation matrix using corrplot(). Use the alphabetic clustering order for the correlated pairs of variables. The text color (color of variables’ labels) in the correlation matrix should be green.

Tip 6: For the illustrative example of the correlation matrix design with corrplot() please check the script for Seminar 7.

```{r}
library(corrplot)
corrplot(all_matrix, order = "alphabet", tl.col="green")
```
4. Remove statistically insignificant correlation coefficients from the correlation matrix:

i.  at p=0.05
ii. at p=0.01

```{r}
corrplot(all_matrix, type="upper", order="alphabet", tl.col = "green", p.mat = all_matrix, sig.level = 0.05, insig = "blank")
### for some reason it says that none of them is statistically significant
```

```{r}
corrplot(all_matrix, type="upper", order="alphabet", tl.col = "green", p.mat = all_matrix, sig.level = 0.01, insig = "blank")
```

```{r}
#install.packages("Hmisc")
```

```{r}
library(Hmisc)
matrix = rcorr(as.matrix(all_data_new))
corrplot(matrix$r, type="upper", order="alphabet", tl.col = "green", p.mat = matrix$P, sig.level = 0.05, insig = "blank")
```
```{r}
corrplot(matrix$r, type="upper", order="alphabet", tl.col = "green", p.mat = matrix$P, sig.level = 0.01, insig = "blank")
```
```{r}
write.csv(All_data_cleared, "All_data_cleared_2.csv")
```


