---
title: "Seminar 13"
author: "Aleksei Sorbale"
date: "2023-05-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("tseries")
```


```{r}
library(plm) 
library(readr)
library(car)     
library(gplots) 
library(tseries)   
library(lmtest)  
```

## Task 1. Data preparation

```{r}
dataPanel<-read_csv("https://github.com/ds777/sample-datasets/blob/master/dataPanel101.csv?raw=true")
attach(dataPanel)
colnames(dataPanel)=c("country", "year", "income", "income_binary", "governance_index", "stability_index", "freedom_index", "opinion")

dataPanel <- pdata.frame(dataPanel, index=c("country", "year"))
dataPanel.
#set the data as panel
```

## Task 2. Data exploration: general heterogeneity

The bars at top indicate the countries' position from left to right starting on the bottom row.

```{r}
coplot(income ~ year|country, type="b", data=dataPanel)#type=b: bivariate, e.g. for two conditions (time and country) at once

```

## Task 3. Panel data modelling. Country effects

### Task 3.1. OLS regression, which is not controlling for heterogeneity across countries and time

**Option 1**

```{r}
ols <-lm(income ~ governance_index + freedom_index + stability_index, data = dataPanel)
summary(ols)
```

**Option 2**

```{r}
pool <- plm(income ~ governance_index + freedom_index + stability_index, data=dataPanel, model="pooling")
summary(pool)
```

### Task 3.2. Fixed effects model, which does consider heterogeneity across countries

`Assumption`: the individual effects of countries are fixed, i.e. country-specific effects are correlated with the independent variables

```{r}
fixed <- plm(income ~ governance_index + freedom_index + stability_index, data=dataPanel, model="within")
summary(fixed)
```

Does model with country-fixed effects have better fit comparing to basic OLS?

**H0**: The fit of basic OLS model is better than the one of the model with country-fixed effects.

If p\<0.05, **one can reject** H0

```{r}
pFtest(fixed, ols)
```

### Task 3.3. Random effects model, which does consider heterogeneity across countries

`Assumption`: the individual effects of countries are random, i.e. country-specific effects are NOT correlated with the independent variables

```{r}
random <- plm(income ~ governance_index + freedom_index + stability_index + factor(year), data=dataPanel, model="random")
summary(random)
```

### Task 3.4. Which model is better: with fixed or random effects?

**H0**: country-specific standard errors are NOT correlated with the IVs -\> random effects model is better than the fixed effects model

```{r}
phtest(fixed, random)
```

## Practice. Productivity in the US

1\. Import the dataset `productivity.csv`(delimiter: `sep=","`)

```{r}
Productivity<-read.csv('C:/Users/.../productivity.csv', sep=',')
```

2\. Set the data as panel. Effects to control: `STATE` and `YR`

3\. Build the following OLS model. DV: `GSP`, IVs: `PC`, `HWY`, `P_CAP`, `UNEMP`

**Legend**:

`P_CAP` = public capital

`HWY` = highway capital

`PC` = private capital

`GSP` = gross state product

`UNEMP` = unemployment rate

4\. Build fixed effects model, which does consider heterogeneity across the US states

5\. Compare the fixed effects model with the basic OLS (from point 3) to understand, which model is better

6\. Build random effects model, which does consider heterogeneity across the US states

7\. Compare the fixed effects model with the random effects model to understand, which model is better