---
title: "Seminar 6"
author: "Aleksei Sorbale"
date: "2023-02-25"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1. Chi-Square Test of Independence (Association)

**Example 1**. US Presidential elections

The survey done in the US before the 2020 Presidential elections shows
the following proportions of the electoral preferences of voters in
Texas and California:

|           | California | Texas |
|-----------|------------|-------|
| **Trump** | 2827       | 3738  |
| **Biden** | 5071       | 1494  |

**Question**: Is the parameter of living in a particular state
associated with the parameter of voting preferences?

**H0**: There is no association between the parameters (the parameters
are independent)

```{r}
#Insert the data
Trump_prop<-c(3738, 2827)#Trump voters proportion in the samples of Texas and California
Biden_prop<-c(1494, 5071)#Biden voters proportion in the samples of Texas and California
US_table<-rbind(Trump_prop, Biden_prop)# rbind() combines vectors into matrix by rows
colnames(US_table)<-c("Texas", "California")
rownames(US_table)<-c("Trump", "Biden")
US_table
```

Calculate chi-squared

```{r}
chisq.test(US_table, correct=F)# correct=F: remove the Yates' correction
```

Get the hypothetical (expected) values (no association between the
parameters)

```{r}
#Option 1
chisq_US<-chisq.test(US_table)
chisq_US$expected

#Option 2
#A package with which one can get extended output of the chi-squared test
library(gmodels)
CrossTable(US_table, expected=T)#"expected=T" = hypothetical values will be included in the table
```

**Example 2**. Arab spring

Hoffman M., Jamal A. 2014. Religion in the Arab Spring: Between Two
Competing Narratives. *Journal of Politics*, vol.76, N3, p. 599

**H0**: In Egypt there is no association between Qur'an reading and
participation in the protests

**Insert the data for Egypt**

```{r}
Protest<-c(52,71,326,339,192)
No_protest<-c(3,10,67,63,46)
religion_protest<-rbind(Protest,No_protest)
colnames(religion_protest)<-c("Never reading", "Rarely reading", "Sometimes reading", "Frequent Reading", "Always reading")
rownames(religion_protest)<-c("Protest", "No protest")
religion_protest
```
```{r}
install.packages("gplots")
```

**Graphical display of the cells' magnitude (contengency table)**

```{r}
library(gplots)
Egypt_visual <- as.table(religion_protest)
balloonplot(Egypt_visual, main ="Association between Qur'an reading and protesting in Egypt", xlab ="", ylab="", label = T, show.margins = F)

Egypt_visual
```

**Calculate chi-squared**

```{r}
chisq.test(religion_protest, correct=F)

```

**Get the hypothetical values**

```{r}
chisq_Egypt<-chisq.test(religion_protest, correct=F)
chisq_Egypt$expected
round(chisq_Egypt$expected)#round the hypothetical values
```

## Task 2. Chi-Square Test of Goodness-Of-Fit

Within one month we observe 10 tiktokers making videos with a popular
challenge. The observable proportion of videos is as follows:

| Tiktoker 1 | Tiktoker 2 | Tiktoker 3 | Tiktoker 4 | Tiktoker 5 | Tiktoker 6 | Tiktoker 7 | Tiktoker 8 | Tiktoker 9 | Tiktoker 10 |
|----------|----------|----------|----------|----------|----------|----------|----------|----------|-----------|
| 16         | 10         | 3          | 9          | 19         | 12         | 4          | 1          | 5          | 10          |

**Q1**: Do the tiktokers make equal proportion of videos with a popular
challenge?

**H0**: There is no significant difference between the observed
proportion and the expected equal proportion.

```{r}
Tiktokers<-c(16,10,3,9,19,12,4,1,5,10)
Tiktokes_prop <- chisq.test(Tiktokers, p = c(1/10, 1/10, 1/10, 1/10, 1/10, 1/10, 1/10, 1/10, 1/10, 1/10))
Tiktokes_prop
```

**Q2**: Is there statistically significant difference between the
observed and expected proportions of tiktoks?

**H0**: There is no significant difference between the observed and the
expected proportions.

Expected proportions for best tiktokers:

| Tiktoker 1 | Tiktoker 2 | Tiktoker 5 | Tiktoker 5 | Tiktoker 10 |
|------------|------------|------------|------------|-------------|
| 3/10       | 1/10       | 3/10       | 2/10       | 1/10        |

```{r}
Tiktokers_best<-c(16,10,19,12,10)
Tiktokes_prop_best <- chisq.test(Tiktokers_best, p = c(3/10, 1/10, 3/10, 2/10, 1/10))
Tiktokes_prop_best
```

## Practice. Oceania at war (or not?)

Big Brother made a survey in Oceania concerning the opinion of male and
female citizens on the war with Eurasia.

1.  Use the survey data to create a matrix:

    1.1. Matrix rows: At war, Not at war, Doubt

    1.2. Matrix columns: Men, Women

    1.3. Proportions for men and women to use to create vectors:

    Men: At war: 34; Not at war: 66; Doubt: 14

    Women: At war: 19; Not at war: 71; Doubt: 13

    1.4. Unify vectors for Men and Women into matrix

    1.5. Use the labels from 1.1. and 1.2. to give names to the columns
    and rows of the matrix
    
```{r}
men <- c(34, 66, 14)
women <- c(19, 71, 13)
matrix_data <- cbind(men, women)
colnames(matrix_data) <- c("Men", "Women")
rownames(matrix_data) <- c("At war", "Not at war", "Doubt")
matrix_data
```
    

2.  **H0**: There is no statistically significant association between
    the parameters of gender and opinion on the war. Calculate the
    chi-squared of independence to test this hypothesis
    
```{r}
chisq.test(matrix_data, correct = F)
```
    

3.  Get the hypothetical values (proportion) for the test

```{r}
expected_values<-chisq.test(matrix_data, correct=F)
expected_values$expected
```


4.  Round the hypothetical values (proportion) for the test

```{r}
round(expected_values$expected)
```


5.  Get extended chi-squared output with `CrossTable()`
```{r}
install.packages("gmodels")
```

```{r}
library(gmodels)
CrossTable(matrix_data, expected = T)
```

