---
title: "Seminar 1"
author: "Aleksander Konkin"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**In this section you can leave comments/description to your operations if necessary**

Another option is to use the sign \# to leave comments

```{r}
### R as calculator. Mathematical symbols: +, -, *, /, ^
"france"
1+1
2-1
4/2
4^2
print(2^2)
```

```{r}
### R as calculator. Mathematical functions: sqrt(), sum(), log(), log10(), log2(), log(x, base = y)

sqrt(121)
sum(12,13,14,15)
log(10)
log10(100)
log(1, base=10)
```

**Help call commands** if you forget something: *help( )*, *?*

```{r}
help(sum)
?print
```


**Assignment operators**: \<-, =

Methods for **manual data entry** in R: function *c( )*

# Task 1

Calculate ENP for the 2011 Duma elections using the formula by G.V.Golosov (2011)
```{r}
# First option
index_2011<-c(0.4931,0.1919,0.1325,0.1168,0.0343,0.0097,0.006)
sum(index_2011/(index_2011+max(index_2011)^2-index_2011^2))
```


```{r}
# Second option
sum_index_2011<-0
for(i in index_2011)#for...in expression loop
	{sum_index_2011<-(i/(i+max(index_2011)^2-i^2))+sum_index_2011
}
sum_index_2011
```

```{r}
getwd()# get the current working directory
setwd()# set the new working directory
```

# Task 2

[Creating and presenting tables]{.underline}: functions *data.frame( )*, *colnames( )*, *rownames( )*

```{r}
data_1<-c(1:5)
data_2<-c(6:10)
table_1<-data.frame(data_1,data_2)
colnames(table_1)<-c("Group 1", "Group 2")#give names to table columns 
rownames(table_1)<-c("Digit 1", "Digit 2", "Digit 3", "Digit 4", "Digit 5")#give names to table rows
table_1
```

# Practice

I. Create a [table with Russian cities]{.underline}

|                |        |                |       |           |             |             |
|-----------|:---------:|:-----------:|:---------:|:---------:|:----------:|:----------:|
| **City**       | Moscow | St. Petersburg | Kazan | Volgograd | N. Novgorod | Vladivostok |
| **District**   |  CFD   |      NWFD      |  VFD  |    SFD    |     VFD     |    FEFD     |
| **Population** | 12500  |      5600      | 1243  |   1013    |    1257     |     605     |

```{r}

```


II. Create a formula for calculating standard deviation (sd) for samples with the following characteristics:


Sample 1. values = 1, 101, 201, 34, 56, 70, 11, 15, 2, 3. n = 10
Sample 2. values = 44, 55, 66, 77, 88, 99, 111, 22, 33, 44, 55, 55, 66, 77, 88. n = 15
Sample 3. values = 0, 1, 2, 3, 5, 4, 7, 8. n = 8
Sample 4. values = 112, 1, 36, 34, 33, 32, 31, 35, 29, 14, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10. n = 20
Sample 5. values = 0.5, 0.44, 0.12, 6, 0.1, 7, 1, 0.15, 2, 0.22. n = 10
Tip: to check the correctness of your formula, you can use the sd() function for the respective set

```{r}

```


III. Create a table presenting the calculation results. The table should contain the columns in the following order: “Sample name” (Sample 1, Sample 2, etc.), “sd”, “Number of observations”.

```{r}

```

