```{r}
library(readr)
All_data_cleared <- read_csv("~/0_HSE_study/колы/training_8/Data/All_data_cleared.csv")
All_data_cleared
```
```{r}
All_data_cleared$`Development Index` <- (All_data_cleared$`Political Stability` + All_data_cleared$`Government Effectiveness` + All_data_cleared$`Rule of Law`) / 3
All <- select(All_data_cleared, -3, -4, -5)
All
attach(All)
```
```{r}
# Regression 1: Political Rights - Development Index
model1 <- lm(`Political Rights` ~ `Development Index`)
summary(model1)
```
For the Political Rights - Development Index model, the independent variable (Development Index) is significant at the 0.001 level (p-value: 9.803e-12). The coefficient estimate of Development Index is 10.822, indicating a positive relationship between Development Index and Political Rights. The model explains 64.69% of the variability in the dependent variable, and the F-statistic indicates that the model has predictive capability.

```{r}
# Regression 2: Civil Liberties - Development Index
model2 <- lm(`Civil Liberties` ~ `Development Index`)
summary(model2)
```
For the Civil Liberties - Development Index model, the independent variable (Development Index) is significant at the 0.001 level (p-value: 3.438e-15). The coefficient estimate of Development Index is 15.251, indicating a positive relationship between Development Index and Civil Liberties. The model explains 75.13% of the variability in the dependent variable, and the F-statistic indicates that the model has predictive capability.

```{r}
# Regression 3: GDP per capita - Development Index
model3 <- lm(`GDP per capita` ~ `Development Index`)
summary(model3)
```
For the GDP per capita - Development Index model, the independent variable (Development Index) is not significant at the 0.05 level (p-value: 0.2824). The coefficient estimate of Development Index is 1.654e+11, indicating a positive relationship between Development Index and GDP per capita. The model explains only 2.563% of the variability in the dependent variable, and the F-statistic indicates that the model does not have predictive capability.

```{r}
# Regression 4: Population growth - Development Index
model4 <- lm(`Population growth` ~ `Development Index`)
summary(model4)
```
For the Population growth - Development Index model, the independent variable (Development Index) is significant at the 0.001 level (p-value: 2.021e-05). The coefficient estimate of Development Index is 0.5478, indicating a positive relationship between Development Index and Population growth. The model explains 33.51% of the variability in the dependent variable, and the F-statistic indicates that the model has predictive capability.

```{r}
library(ggplot2)

# Scatterplot for Civil Liberties vs. Development Index
cl <- ggplot(data = All, aes(x = `Development Index`, y = `Civil Liberties`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Development Index") +
  ylab("Civil Liberties") +
  ggtitle("Relationship between Development Index and Civil Liberties")
cl
# Scatterplot for Political Rights vs. Development Index
pr <- ggplot(data = All, aes(x = `Development Index`, y = `Political Rights`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Development Index") +
  ylab("Political Rights") +
  ggtitle("Relationship between Development Index and Political Rights")
pr
# Scatterplot for GDP per capita vs. Development Index
gp <- ggplot(data = All, aes(x = `Development Index`, y = `GDP per capita`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Development Index") +
  ylab("GDP per capita") +
  ggtitle("Relationship between Development Index and GDP per capita")
gp
# Scatterplot for Population growth vs. Development Index
pg <- ggplot(data = All, aes(x = `Development Index`, y = `Population growth`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Development Index") +
  ylab("Population growth") +
  ggtitle("Relationship between Development Index and Population growth")
pg
```
```{r}
par(mfrow=c(2,2)) # create a 2x2 grid of plots

# plot 1
plot(All$`Development Index`, All$`Civil Liberties`, 
     xlab = "Development Index", ylab = "Civil Liberties", 
     main = "Civil Liberties model")
abline(lm(`Civil Liberties` ~ `Development Index`, data = All), col = "red") # add regression line

# plot 2
plot(All$`Development Index`, All$`Political Rights`, 
     xlab = "Development Index", ylab = "Political Rights", 
     main = "Political Rights model")
abline(lm(`Political Rights` ~ `Development Index`, data = All), col = "red") # add regression line

# plot 3
plot(All$`Development Index`, All$`Population growth`, 
     xlab = "Development Index", ylab = "Population growth", 
     main = "Population growth model")
abline(lm(`Population growth` ~ `Development Index`, data = All), col = "red") # add regression line

# plot 4
plot(All$`Development Index`, All$`GDP per capita`, 
     xlab = "Development Index", ylab = "GDP per capita", 
     main = "GDP per capita model")
abline(lm(`GDP per capita` ~ `Development Index`, data = All), col = "red") # add regression line

```
```{r}
library(cowplot)
plot_grid(cl, pr, pg, gp)
```

