---
title: "Seminar 14"
author: "Aleksei Sorbale"
date: "2023-05-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nnet)
```

## Task 1. Prepare the data for logistic regression

```{r}
library(readr)
opinion_2012 <- read_delim("~/0_programming/0_prog/0_HSE_study/колы/14/Data/data2012_mneniye.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
attach(opinion_2012) 
```

In the column `Vote` 1 means voting for Zhirinovsky; 2 -- for Zyuganov; 3 -- for Mironov; 4 -- for Prokhorov; 5 -- for Putin

In the column `Gender` 2 means female, 1 -- male

**What factors increase the probability of voting for Putin?**

Let us check the factors related to gender, age and willingness to participate in the protests

But firstly **filter the data, remove the NAs**.

```{r}
opinion_new<-as.data.frame(cbind(Gender, Vote, Age, Protest))
opinion_new_NAs<-na.omit(opinion_new)
attach(opinion_new_NAs)
```

## Task 2. Data calibration for logistic regression

Set the vote for Putin as 1, and for the rest -- as 0

```{r}
putin_one<-ifelse(Vote==5, 1, 0)
```

Set the willingness to participate in protest actions as 1, and the absence of such willingness as 0

```{r}
Protest_one<-ifelse(Protest==1, 1, 0)
```

Gender: 1 -- female, 0 -- male (in the initial data set, female was designated as 2, and male as 1)

```{r}
Gender_one<-ifelse(Gender==2, 1, 0)
```

## Task 3. Logistic regression

Run two logistic regressions

```{r}
putin_glm_1<-glm(putin_one ~ Gender_one + Age + Protest_one, data=  opinion_new_NAs, family = binomial(link = "logit"))
summary(putin_glm_1)

putin_glm_2<-glm(putin_one ~ Gender_one  + Protest_one, data= opinion_new_NAs, family = binomial(link = "logit"))
summary(putin_glm_2)
```

**Calculate the log-likelihood value**

```{r}
logLik(putin_glm_1) 

logLik(putin_glm_2)
```

The bigger the log-likelihood value, the better the model in terms of predictive capability

### Task 3.1. Predicted probabilities

Two methods for calculating the model's predicted probabilities for regression coefficients

**Method 1**

```{r}
prob_putin<-fitted(putin_glm_1) 

prob_putin
```

**Method 2**

```{r}
prob_putin_2<-predict(putin_glm_1, type = "response") 

prob_putin_2
```

**Make the combinations for predicted probabilities more illustrative**

```{r}
opinion_modified<-data.frame(Vote, putin_one, Gender_one, Age, Protest_one, prob_putin)
opinion_modified
```

### Task 3.2. Odds ratio

```{r}
exp(coef(putin_glm_1)) # Method 1
exp(putin_glm_1$coefficients) # Method 2
```

`OR>1` for beta-coefficient = IV is valid for the prediction of DV taking the value of 1

**Calculate confidence intervals for odds ratio**

```{r}
exp(confint(putin_glm_1))
```

## Practice. Voting for Zhirinovskii

1.  Filter the data, so that only the variables `Gender`, `Vote`, `Education` and `Protest` remain

2.  Remove the NAs.

3.  Prepare the variables:

    3.1. Set the vote for `Zhirinovskii` as 1, and for other candidates as 0.

    3.2. Set the `willingness to participate in protest activities` as 1, and the absence of such willingness as 0.

    3.3. Set female in the `Gender` variable as 1, male - as 0.

    3.4. Leave `Education` variable as it is.

4.  Create the logistic regression model: DV = vote for `Zhirinovskii`, IVs = `Willingness to participate in the protests`, `Gender`, `Education`

5.  Calculate the predicted probabilities for the model. Put them into dataframe for better illustration.

6.  Calculate odds ratio.

7.  Calculate confidence intervals for odds ratio.