---
title: "Seminar 10"
author: "Aleksei Sorbale"
date: "2023-04-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1. Paired regressions

```{r}

library(car)
library(ggplot2)
```
```{r}
library(readr)
data <- read_delim("C:/Users/Alex/OneDrive/Документы/0_programming/0_prog/0_HSE_study/колы/10/Data/happiness.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
data
attach(data)
```


```{r}

mod1 <- lm(happy ~ GINI)
summary(mod1)

mod2 <- lm(happy ~ god_imp)
summary(mod2)
```

## Task 2. Additive model and model with interaction effect

```{r}

mod.additive<-lm(happy ~ GINI + god_imp)
summary(mod.additive)

mod.interaction<-lm(happy ~ GINI*god_imp)#with "*" the interaction effect is set
summary(mod.interaction)
```

## Task 3. Diagnostics of the model with interaction effect

Determine which model is better in terms of explanation and prediction with `performance` package

```{r}

library(performance)
compare_performance(mod1, mod.additive, mod.interaction)
```

Plot for interaction effect: `interplot`

```{r}
#install.packages("interplot")
library(interplot)
interplot(m = mod.interaction,
           var1 = "GINI",
           var2 = "god_imp",  hist = T) +
  xlab("Religiosity") +
  ylab("Marginal effect of inequality on the level of happiness") +
  geom_hline(yintercept = 0, linetype="dashed") +
  geom_vline(xintercept = 0, linetype="dashed")
```

Determine the interval of values of the moderator (`god_imp`), for which the interaction is significant (**does exist**)

```{r}
#install.packages("interactions")
library(interactions)
options(width = 60)
johnson_neyman(mod.interaction,
               pred = "GINI",  modx = "god_imp",  alpha = 0.05)
```

## Practice. Reaction to the process of European integration

1\. Import the dataset `ESS2016.csv`

2\. Filter the dataset so that only the following variables remain: `euftf`, `imwbcnt`, `polintr`

3\. Build the additive model: DV = `euftf`, IV1 = `imwbcnt`, IV2 = `polintr`

4\. Build the model with the interaction effect: DV = `euftf`, IV (predictor) = `imwbcnt`, Z (moderator) = `polintr`

5\. Compare the fit of additive model and interaction model

6\. Build a plot of the interaction effect. Add captions to the plot's axes

7\. Determine the interval of values of the moderator, for which the interaction is significant. Add a Johnson-Neyman plot for illustration

**Codes**:\

`euftf`: European unification go further or gone too far

`imwbcnt`: Immigrants make country worse or better place to live

`polintr`: How interested in politics the person is

```{r}

#ESS<-read.csv("C:/Users/User/.../ESS2016.csv", sep=";")
```